biology

### 2020-07-22 documents/acknowledgement.tex
Protobuf
paper or whatever

@@

Dr. Dainis' videos on microbiological technique were also useful.

Thanks to the professors at York and beyond for returning my emails.

Thanks to L.H. for wisdom regarding this project.

Thanks to P.B and H.P. for tolerating ramblings and M. for the hug.

Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical. Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.

@@

@@

>>>>

This paper would have been absolutely impossible without the support of hundreds of open-source software packages, ranging from monolithic industry-supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca. Thank you to all the dedicated authors that develop and maintain these tools.

@@

Dr. Dainis' videos on microbiological technique were also useful. The Thought Emporium's videos on PCB prototyping and

Thanks to all the professors at York and beyond for returning my emails and checking their biofridges.

Thanks to L.H. for wisdom regarding this project; P.B and H.P. and ice9 for tolerating midnight ramblings and M.Q. for the hug.

Special thanks to all the people - all equally capable of writing this paper if provided the opportunity - who circumstance led to work menial shifts at the component suppliers that remained open that were so critical. Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.

@@

\rule{\linewidth}{0.2pt}

The authors acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for developing and making the AustinMan and AustinWoman human body models available at https://sites.utexas.edu/austinmanaustinwomanmodels/.

\rule{\linewidth}{0.2pt}

@@

{\Large <3}

### 2020-07-22 documents/paper.tex
paper or whatever

This may account for why this paper has been ignored.

@@

@@

@@

@@

\clearpage
\paragraph{\textbf{Time dependence}}\

@@

%\printbibliography[ title={Other references}]

>>>>

This may account for why this paper has been largely ignored.

@@

\clearpage
{\Large \it The contenders}\\

Protein net charges extracted from protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.

@@

\paragraph{Time-domain modulation}

@@

\clearpage
{\Large \it Time-dependence}\\

@@

@@

\printbibliography[ title={All references}]

### 2020-07-22 documents/supplemental.tex
paper or whatever

@@

An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:

This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.

Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.

However, I think this person may have missed out. Learning

So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively. I have often found that I learn greatly from working on the projects of others.

We present this only as a cautionary tale in the hopes that someday I will listen.

>>>>

\includepdf[
%% Include all pages of the PDF
pages=-,
%% make this page have the usual page style
%% (you can change it to plain etc). By default pdfpages
%% sets the pagecommand to \pagestyle{empty}
pagecommand={\thispagestyle{empty}},  
%% Add a "section" entry to the ToC with the heading
%% "Quilling Shapes" and the label "sec:shapes"
addtotoc={1,section,1,Quilling Shapes,sec:shapes}]
%% The pdf file itself
{biology.pdf}

@@

\rule{\linewidth}{0.2pt}
%
%An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
%
%
%
%This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
%
%Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
%
%However, I think this person may have missed out. Learning 
%
%So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively. I have often found that I learn greatly from working on the projects of others.
%
%We present this only as a cautionary tale in the hopes that someday I will listen.
